Manuscript

### 2014-08-31 inst/simulation/manuscript.Rmd
...

context <- Context$new(resultDataDirectory=wd.data.results, processedDataDirectory=wd.data.processed, rawDataDirectory=wd.data.raw, scratchDirectory=wd.scratch, figuresDirectory=wd.figures)
scenarios <- c("A","B","C","D","E","F")
modelNames <- c(paste("SmoothModel", "nbinomial", "matern", "ar1", sep = "-"))
iterations <- as.integer(c(1,1,1,1,3,1))

@@

```{r figure-3}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)
p <- ggplot(populationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point() + stat_smooth(method="lm", colour="black") +
  scale_colour_manual("Model", values=c("black", "darkgray"), labels=c("ST", "T")) +
  geom_abline(colour="darkgrey", linetype="longdash") + facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3.png", width=8, height=4)
```

```{r figure-4-test, eval=FALSE}
study <- getStudy(scenario="F")
validation <- Validation(study=study)
x <- validation$validateSpatialPopulationSize(modelNames[1])
```

```{r figure-4}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelNames)
p <- ggplot(populationCorrelations, aes(True, Correlation, colour=modelName)) + geom_point() +
  scale_colour_manual("Model", values=c("black", "darkgray"), labels=c("ST", "T")) +
  facet_wrap(~Scenario) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4.png", width=8, height=4)
```

```{r figure-5-init}

```

```{r figure-5}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
a <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)
p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("black", "darkgray"), labels=c("ST", "T")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario")
print(p)
saveFigure(p, "manuscript-figure-5.png", width=4, height=2)
```

>>>>

context <- Context$new(resultDataDirectory=wd.data.results, processedDataDirectory=wd.data.processed, rawDataDirectory=wd.data.raw, scratchDirectory=wd.scratch, figuresDirectory=wd.figures)
scenarios <- c("A","B","C","D","E","F")
modelNames <- c(paste("SmoothModel", "nbinomial", "matern", "ar1", sep = "-"), paste("SmoothModel", "nbinomial", "ar1", sep = "-"))
iterations <- as.integer(c(1,1,1,1,3,1))

@@

```{r figure-3}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)
validation$summarizePopulationSize(populationSizes)

p <- ggplot(populationSizes, aes(Observed, Estimated, colour=modelName)) + geom_point(size=1) + stat_smooth(method="lm", aes(colour=modelName), se=F) +
  scale_colour_manual("Model", values=c("darkgray","black"), labels=c("T", "ST")) +
  geom_abline(colour="darkgrey", linetype="longdash") + facet_wrap(~Scenario, scales="free") +
  xlab("True population size") + ylab("Estimated population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
print(p)
saveFigure(p, "manuscript-figure-3.png", width=8, height=4)
```

```{r table-1}
ddply(populationSizes, .(Scenario, modelName), function(x) {
  y <- lm(Estimated~Observed, x)
  data.frame(Intercept=round(coef(y)[1], 0), Slope=round(coef(y)[2], 2))
})
```

```{r table-2}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
failedEstimations <- validation$countFailedEstimations(modelNames=modelNames)
failedEstimations$pFailed <- (1 - failedEstimations$nEstimated / 50) * 100
failedEstimations
```

```{r figure-4-test, eval=FALSE}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
x <- validation$validateSpatialPopulationSize(modelNames[1])
```

```{r figure-4}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(modelNames=modelNames[1])

p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
print(p)
saveFigure(p, "manuscript-figure-4.png", width=4, height=4)
```

```{r figure-5}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
a <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5.png", width=4, height=2)
```
